A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-10-01 paper/paper.tex
more

\paragraph{Link to classical RL algorithms.}
Note that most RL algorithms, including \textit{Temporal Difference (TD)} learning [Sutton et al.,
  Bertsekas] and SARSA can be cast in this general variational framework. For example TD can corresponds
to the above framework with a linear value approximator with feature encoding $\phi(s,a) = \delta_{(s,a)} =  \text{ point mass at }(s,a)$,
and so $$\nabla_{\theta^Q_{k+1}}Q(s, a|\theta^Q_{k+1}) = \phi(s, a) = \delta_{(s,a)}$$
...

>>>>

\paragraph{Link to classical RL algorithms.}
Note that most RL algorithms, including \textit{Temporal Difference (TD)} learning [Sutton et al.,
  Bertsekas] and SARSA can be cast in this general variational framework. For example TD can corresponds
to the above framework with a linear value approximator with feature encoding $\phi(s,a) = \delta_{(s,a)} =  \text{ point mass at }(s,a)$
on the grid $\mathcal S \times \mathcal A$,
and so $$\nabla_{\theta^Q_{k+1}}Q(s, a|\theta^Q_{k+1}) = \phi(s, a) = \delta_{(s,a)}$$
...
